Seagrass mapping and monitoring along the coasts of Crete, Greece

### 2011-01-31 MScDiplom_Lemenkova.tex
added 'Supervisory Committee', 'Course Title' as sections

\begin{document}

\pagenumbering{roman}

\title{Seagrass mapping and monitoring along the coasts of Crete, Greece}
\author{by Lemenkova Polina}
\date{\today}
\maketitle
\pagebreak

\textbf{Course Title:} \\
{Geo-Information Science and Earth Observation for Environmental Modelling and Management}\\

\textbf{Level} \hfill{Master of Science (MSc)}\\
\textbf{Course Duration:} \hfill{September 2009 – March 2011}\\
\textbf{Consortium partners:} \\

@@

\begin{center}
\textbf{Seagrass mapping and monitoring along the coasts of Crete, Greece}\\
\vspace{1em}
 {by Lemenkova Polina}
\end{center}

@@

\textbf{Thesis Assessment Board}:
\begin{itemize}
	\item Name Examiner 1 (Chair)
	\item Name Examiner 2
	\item External Examiner \hfill{Dr. \textit{Petter Pilesj\"o} (Lund University, GIS Centre)}
\end{itemize}

@@

\textbf{Member Supervisors}: \\
\begin{itemize}
	\item[* ] Mr. \textit{Valentijn Venus} (Department of Natural Resource, ITC)
	\item[* ] Dr. \textit{Albertus G. Toxopeus} (Department of Natural Resource, ITC)
\end{itemize}

@@

		Signed.................................(Lemenkova Polina) \\

>>>>

\begin{document}
\pagenumbering{roman}

\begin{titlepage}
	\centering
	\title{Seagrass mapping and monitoring along the coasts of Crete, Greece}
	\author{by Lemenkova Polina}
	\date{\today}
	\maketitle	
\end{titlepage}
\pagebreak

\section*{}
\addcontentsline{toc}{section}{Course Title}
\textbf{Course Title} \\
{Geo-Information Science and Earth Observation for Environmental Modelling and Management}\\

\textbf{Level} \hfill{Master of Science (MSc)}\\

\textbf{Course Duration:} \hfill{September 2009 – March 2011}\\

\textbf{Consortium partners:} \\

@@

\section*{}
\addcontentsline{toc}{section}{Supervisory Committee}
\begin{center}
\textbf{Seagrass mapping and monitoring along the coasts of Crete, Greece}\\
\vspace{1em}
 {by Lemenkova Polina}
\end{center}

@@

\textbf{Thesis Assessment Board}:
\begin{itemize}
	\item Name Examiner 1 (Chair)\dotfill
	\item Name Examiner 2\dotfill
	\item External Examiner \dotfill \\ \hfill{Dr. \textit{Petter Pilesj\"o} (Lund University, GIS Centre)}
\end{itemize}

@@

\textbf{Member Supervisors}: \\
\begin{itemize}
	\item[* ] Mr. \textit{Valentijn Venus} \dotfill \\ (Department of Natural Resource, ITC)
	\item[* ] Dr. \textit{Albertus G. Toxopeus} \dotfill \\ (Department of Natural Resource, ITC)
\end{itemize}

@@

		Signed................................(Lemenkova Polina) \\
